\documentclass[a4paper, 11pt]{article}
\input{preamble.tex}

\begin{document}

\maketitle
\begin{center}See GitHub repo at:\\
{\Large \url{https://github.com/frederikgantriis/AuctionSystem-DISYS}}
\end{center}

\section{Introduction}
%A short introduction to what you have done.
This is an auction system, where different clients bid on an auction, managed by servers. The systems consists of 3 servers and n clients. These servers work as replica managers in an active replication system. Clients can join and leave whenever they want. Up to one servers can fail, with the systems still running correctly. Equally, if all three servers are running correctly, a client would be able to loose connection to any server and still both read (get results) and write (bid) from and to the servers.

\section{Architecture}
% A description of the architecture of the system and the protocol (behaviour), including any protocols used internally between nodes of the system.
We have made an auction-system using Active replication. In this instance, we have a client/front-end that communicates to all the available servers (the replication managers in this instance).

\section{Correctness 1}
%Argue whether your implementation satisfies linearisability or sequential consistency (after precisely defining  the property it satisfies).
Sequential consistency is a property of a system that appears to only contain a single copy of data. 


\section{Correctness 2}
%An argument that your protocol is correct in the absence and the presence of failures.

\end{document}
